---
title: "Shiraz A Sabah's CV"
author: Shiraz A Sabah
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

My_GS <- scholar::get_profile("uPg-O4YAAAAJ") 

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1WKzFXByG0MFgV6GuYAoEvNdv6NJqxAoc0eGi7Alu7H8/edit?usp=sharing",  
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
# datadrivencv::build_network_logo(CV$entries_data)
```


```{r}
if(params$pdf_mode){
  cat("View this CV online with links at https://github.com/shirazsabah/cv/blob/main/cv.html")
} else {
  cat("[<i class='fa fa-download'></i> Download a PDF of this CV](https://github.com/shirazsabah/cv/blob/main/cv.pdf)")
}
```

Contact {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> shiraz.sabah@ndorms.ox.ac.uk
- <i class="fa fa-github"></i> [github.com/shirazsabah](https://github.com/shirazsabah)
- <i class="fa fa-linkedin"></i> [shirazsabah](https://www.linkedin.com/in/shiraz‑sabah‑157863177)
- <i class="fa fa-home"></i> [ndorms.ox.ac.uk/team/shiraz‑sabah](https://www.ndorms.ox.ac.uk/team/shiraz‑sabah)
- <i class="fa fa-twitter"></i> [bonedoc247](https://twitter.com/bonedoc247)
- <i class="fa fa-phone"></i> +44 (0) 7956 534625

- For more information, please contact me via email.


Memberships {#member}
--------------------------------------------------------------------------------

```{r}
CV %>% print_member_info()
```



Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Last updated on `r Sys.Date()`.



Main
================================================================================

Shiraz A Sabah {#title}
--------------------------------------------------------------------------------

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```



Qualifications {data-icon=award data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('qualifications')
```



Prizes {data-icon=trophy data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('prizes')
```



Grants {data-icon=laptop data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('grants')
```



Leadership & Management {data-icon=suitcase data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('management')
```



Employment {data-icon=stethoscope data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('employment')
```



Teaching {data-icon=chalkboard-teacher data-concise=true}
--------------------------------------------------------------------------------

::: aside
```{r}
CV %<>% print_text_block('teaching_aside')
```
:::

```{r}
CV %<>% print_section('teaching')
```



Research {data-icon=chart-line data-concise=true}
--------------------------------------------------------------------------------

::: aside
```{r}
CV %<>% print_text_block('research_aside')
```

Find more information on my Google Scholar profile: `r round(scholar::get_num_articles(My_GS$id), -1)` scientific publications, `r My_GS$total_cites` citations, h-index: `r My_GS$h_index`.

- <i class="fa fa-link"></i> [scholar/shirazsabah](https://scholar.google.co.uk/citations?user=uPg-O4YAAAAJ&hl=en&oi=ao)
:::

```{r}
CV %<>% print_section('research')
```



References {data-icon=book data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('references')
```


```{r}
CV %<>% print_links()
```

